Something about correlation functions

### 2021-06-25 paper-correlations.tex
Some text regarding chord-length function and verification

@@

>>>>

\subsection{Chord length function}
The chord length function $p^{(i)}(\bm{r})d\bm{r}$ is defined as the probability of
finding a chord of length between $|\bm{r}|$ and $|\bm{r} + d\bm{r}|$ and
paralled to $\bm{r}$ in phase $i$. A chords is a line segment between
intersections of an infinitely long line with the two-phase interface. This
function, again, can be calculated by cutting slices from a multidimensional
array. The algorithm is as follows:
\begin{algorithmic}[1]
  \Procedure{chordlength}{$array, phase, nbins$}
    \State $lengths \gets [\quad]$
    \State $ind \gets array = phase$ \Comment{$array$ is compared with $phase$
      element-wise}
    \State $edgephase \gets maximum(array) + 1$ \Comment{``bogus'' phase for the
      interface of the phase $phase$}
    \State $edge \gets edgephase \cdot [\text{Detect edges in $ind$}]$ \Comment{We
      use distance transform here}
    \State $combo = min(edge + array, edgephase)$ \Comment{Combine the original
      array and the interface for the phase $phase$}
    \ForAll{$direction \in \{\text{Requested directions}\}$}
      \ForAll{$slice \in \{\text{Slices parallel to $direction$}\}$}
        \State $len \gets 0$
        \State $startonedge \gets false$
        \ForAll{$x \in slice$}
          \If{$x = edgephase$}
            \Comment{Edge found}
            \If{$len > 1 \land startonedge$}
              \State $lengths \gets (len-1):lengths$
            \EndIf
            \State $len \gets 0$
            \State $startonedge \gets true$
          \ElsIf{$x \ne phase$}
            \State $startonedge \gets false$
          \EndIf
          \State $len \gets len + 1$
        \EndFor
      \EndFor
    \EndFor
    \State Bin elements in $lengths$ to $nbins$ bins to compute a histogram $H$
    \State \textbf{return} $H$
  \EndProcedure
\end{algorithmic}

@@

\section{Verifying our algorithms}
To verify our package we use random datasets of overlapping spheres with radii
$R$ and centers placed in points generated by Poisson point process with a
parameter $\lambda$. For these datasets correlation functions can be given in
closed-form expressions for one-, two- and three-dimensional cases. For the sake
of testing we obtain a collection of spheres in a square (the number of
dimensions $n = 2$) or cube ($n = 3$) with the side $s$ using the following
algorithm:
\begin{algorithmic}[1]
  \Procedure{spheres}{$s, n, R, \lambda$}
    \State $nspheres \gets poisson(\lambda s^n)$ \Comment{$poisson(\lambda)$
      generates random numbers with Poisson distribution with parameter
      $\lambda$.}
    \State Generate $nspheres$ random points which are uniformly distributes in
    a cube ($n = 3$) or square ($n = 2$) with a side $s$
    \State Draw spheres of radius $R$ in those points. Store the result in an
    array $output$.
    \State \textbf{return} $output$
  \EndProcedure
\end{algorithmic}
